Subsegmental language detection in Celtic language text

### 2014-05-09 codeswitch-cltw-2014/codeswitch.tex
methodology+
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@52732 72bbbca6-d526-0410-a7d9-f06f51895060

Once we get the probabilities, our task at hand is to take in the data and process it such that the  sub-segments of code-switched data are detected in it. We collected data from twitter over a period of time and this was filtered into three sets which had been identified to be Irish, Welsh and Breton. To be able to compare with the language model built above in the character n-gram approach, this data is to be processed like it aswell. \\

@@

\section{Results}
\label{sec:results}
As described in the evaluation the techniques were used on a dataset collected over a period of time, for the three language pairs\footnote{\url{http://indigenoustweets.blogspot.in/2013/12/mapping-celtic-twittersphere.html}}. The statics of the same are described in the Table below. //

@@

(CHECKLATER-FORMATTING)

>>>>

Once we get the probabilities, our task at hand is to take in the data and process it such that the  sub-segments of code-switched data are detected in it. We collected data from twitter over a period of time \footnote{\url{http://indigenoustweets.blogspot.in/2013/12/mapping-celtic-twittersphere.html}} and this was filtered into three sets which had been identified to be Irish, Welsh and Breton. To be able to compare with the language model built above in the character n-gram approach, this data is to be processed like it aswell. \\

@@

\section{Results}
\label{sec:results}
As described in the ~\ref{sec:method} the data collected from Twitter for the three language pairs, was processed using the techniques mentioned. The statics of the same are described in ~\ref{table:accuracy}. //

@@
